Followers Are Not Enough: Beyond Structural Communities in Online Social Networks \\Followers Are Not Enough: A Question-Oriented Approach to Community Detection

### 2014-07-30 paper-for_arxiv/methods.tex
fixing influence stuff in intro
consistency in methods

For the activity-based communities, we consider only the timing of each user's tweets and ignore any additional content. From this starting point, we can view the behavior of a user $u$ on Twitter as a point process, where at any instant $t$ the user has either emitted a tweet ($X_{t}(u) = 1$) or remained silent ($X_{t}(u) = 0$). This is the view of a user's dynamics taken in~\cite{ver2012information} and~\cite{darmon2013understanding}. Thus, we reduce all of the information generated by a user on Twitter to a time series $\{ X_{t}(u)\}$ where $t$ ranges over the time interval for which we have data (9 weeks in this case). Because status updates are only collected in discrete, 1-second time intervals, it is natural to consider only the discrete times $t = 1 \text{ s}, 2 \text{ s}, \ldots, $ relative to a reference time. We can then compute the flow of information between two users $u$ and $v$ by computing the transfer entropy between their time series $X_{t}(u)$ and $X_{t}(v).$

For the communities based on transfer entropy, we weight each edge from a user $u$ to a follower $f$ by the estimated transfer entropy of the user $u$ on $f$, 
\begin{align}
	w_{u \to f}^{\text{TE}(k)} = \widetilde{\text{TE}}_{X(u) \to X(f)}^{(k)}. \label{Eqn-EW-activity}
\end{align}
A positive value for the transfer entropy of the user $u$ on $f$ indicates that $u$ influences $f$, or that $u$ and $f$ share a common influencer~\cite{ver2012information}. See Appendix A for a detailed introduction to transfer entropy and its estimation from data.

Operationally, we expect users to interact with Twitter on a human time scale, and thus the natural one-second time resolution is too fine since most humans do not write tweets on the time scale of seconds. We coarsen each time series by considering non-overlapping time intervals ten minutes in length. For each time interval, we record a 1 if the user has tweeted during that time interval, and a 0 if they have not. Thus, the new coarsened time series now captures whether or not the user has been active on Twitter over any given ten minute time interval in our data set. We then compute the transfer entropy on these coarsened time series taking $k$ to range from 1 to 6, which corresponds to a lag of ten minutes to an hour. The choice of lag must balance a trade-off between additional information and sparsity of samples: as we increase the lag, we account for longer range dependencies, but we also decrease the number of samples available to infer a higher dimensional predictive distribution. Ultimately, due to similarities in the underlying communities we chose a lag-4 transfer entropy. All references to activity-based weights, unless otherwise noted, refer to this choice of lag.

>>>>

For the activity-based communities, we consider only the timing of each user's tweets and ignore any additional content. From this starting point, we can view the behavior of a user $u$ on Twitter as a point process, where at any instant $t$ the user has either emitted a tweet ($X_{t}(u) = 1$) or remained silent ($X_{t}(u) = 0$). This is the view of a user's dynamics taken in~\cite{darmon2013understanding} and~\cite{ver2012information}. Thus, we reduce all of the information generated by a user on Twitter to a time series $\{ X_{t}(u)\}$ where $t$ ranges over the time interval for which we have data (9 weeks in this case). Because status updates are only collected in discrete, 1-second time intervals, it is natural to consider only the discrete times $t = 1 \text{s}, 2 \text{s}, \ldots, $ relative to a reference time.

Operationally, we expect users to interact with Twitter on a human time scale, and thus the natural one-second time resolution is too fine since most humans do not write tweets on the time scale of seconds. We coarsen each time series by considering non-overlapping time intervals ten minutes in length. For each time interval, we record a 1 if the user has tweeted during that time interval, and a 0 if they have not. Thus, the new coarsened time series now captures whether or not the user has been active on Twitter over any given ten minute time interval in our data set. We can then compute the flow of information between two users $u$ and $v$ by computing the transfer entropy between their time series $X_{t}(u)$ and $X_{t}(v).$ See Appendix A for a detailed introduction to transfer entropy and its estimation from data.

For the communities based on transfer entropy, we weighted each edge from a user $u$ to a follower $f$ by the estimated transfer entropy of the user $u$ on $f$, 
\begin{align}
	w_{u \to f}^{\text{TE}(k)} = \widetilde{\text{TE}}_{X(u) \to X(f)}^{(k)}. \label{Eqn-EW-activity}
\end{align}
As discussed in the introduction, a positive value for the transfer entropy of the user $u$ on $f$ indicates that $u$ influences $f$, or that $u$ and $f$ share a common influencer~\cite{ver2012information}, and that the time series $X(u)$ and $X(f)$, are casually related in a Granger sense.

 We computed the transfer entropy on each coarsened time series with lag $k$ ranging from 1 to 6, this corresponds to a lag of ten minutes to an hour. The choice of lag must balance a trade-off between additional information and sparsity of samples: as we increase the lag $k$, we account for longer range dependencies, but we also decrease the number of samples available to infer a higher dimensional predictive distribution, see Appendix A for a discussion. Ultimately, due to similarities in the underlying communities we chose a lag-4 transfer entropy. All references to activity-based weights, unless otherwise noted, refer to this choice of lag.
